---
title: "WUP_04"
author: "Gloria Jones"
date: "Summer 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

```{r}
gssdata=read_csv("GSScsv.csv")
```



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(gssdata,aes(x=DEGREE,y=WORDSUM))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The box for LT High school is different from Junior college, and the box of graduate science. The two would be different, because one would slide those three between each other, they would be considered in a different space. With that being said, i believe these results are different.  
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

# Numerical results

```{r}
favstats(WORDSUM~DEGREE,data=gssdata)
```
  
The mean for the bachelor, graduate, junior college are close to being the same. The mean for the HS and LT HS are different from the other schools because their mean is lower and the other schools have a higher mean.  
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
model1 <- aov(WORDSUM~DEGREE,data=gssdata)
summary.aov(model1)
```
  
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 13.2, 2, 2))
plot(TukeyHSD(model1),las=2)
```
  
The categories that are different would be the LT HS graduate and the HS graduate, because both of them don't run into the zero line, those were the only two categories that would be outside of that. However, I am able to see a difference in the graph above.   
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
      
In the beginning of creating my report, I had to fork my file from github, then copy and past the url into rstudio and creat a new project. I then had to upload my credentials and then determine what kind of helper file I needed for this assignment. I went through a series of copying and pasting from the numerical cat. rmd file to my WUP_4 file. I was able to collect all my data to determine the outcome of the report. I had to use two different graphs towards the end of my report. The first one wasn't very clear with the information that I needed to determine the differences. The second graph was clear with information. I was able to analyze and determine the difference between the schools and finish with a conclusion.